---
title: "Chicago Tree Data (DuPage County)"
output: 
  rmarkdown::html_document:
    toc: true
    toc_depth: 4
    theme: yeti
    number_sections: true
    df_print: paged
---

<style>
  .main-container {
    max-width: 1400px !important;
  }
</style>


```{r set-options, echo=FALSE, cache=FALSE}
options(width = 150)
```

```{r include = FALSE}
ctree_raw = read.csv (
      'D:/CRTI/data/SurveyNov2017_canopy_dist.txt',
      as.is = TRUE,
      header = TRUE,
      sep ='\t'
)
ctree_clean = read.csv (
      'D:/CRTI/data/cleaned/dupage_county_accepted_V4.csv',
      as.is = TRUE,
      header = TRUE,
      sep =','
)
```
# Raw data

## DATATYPE
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(ctree_raw$DATATYPE)
barplot(t)
t
```

## STREETTREE
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(ctree_raw$STREETTREE)
```

## GENUSSPECI (top 50)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
df <- as.data.frame(table(ctree_raw$GENUSSPECI))
head(df[order(-df$Freq),],50)
```

## DBH_IN
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$DBH_IN, breaks=c(0,.1,.5,1,2,3,4,5,10,15,20,40,60,80,100),include.lowest = TRUE))
```

## FC_cnsd2 (LU)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(ctree_raw$FC_cnsd2)
barplot(t)
t
```

## Compactnes (CROWN_COMPACTNESS)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$Compactnes, breaks=c(0,seq(.00001, 4,.5)),include.lowest = TRUE))
barplot(t)
t
```

## nDSM_max (HEIGHT_MAX)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$nDSM_max, breaks=c(0,.1, seq(10, 135, 10)),include.lowest = TRUE))
barplot(t)
t
```

## nDSM_mean (HEIGHT_MEAN)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$nDSM_mean, breaks=c(0,.1, seq(10, 135, 10)),include.lowest = TRUE))
barplot(t)
t
```

## Area (CROWN_AREA)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$Area, breaks=c(0,.1, 10, 100, 200, 400, 600, 1000),include.lowest = TRUE))
barplot(t)
t
```

## MEDAGE (BLDG_AGE)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$MEDAGE, breaks=c(0, seq (1950, 2020, 10)),include.lowest = TRUE))
barplot(t)
t
```

## HousingDen (HU_DENS)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$HousingDen, breaks=c(0, 100, 500, 1000, 1500, 2000, 3000, 6000, 9000,12000),include.lowest = TRUE))
barplot(t)
t
```

## RelBord_tr (RELBORDER_TREE)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_raw$RelBord_tr, breaks=seq(0, 1, 0.1),include.lowest = TRUE))
barplot(t)
t
```


# Cleaned data
## DATATYPE
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(ctree_clean$DATATYPE)
t <- c(sum(is.na(ctree_clean$DATATYPE)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

<!-- ## STREETTREE -->
<!-- ```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000} -->
<!-- barplot(table(ctree_clean$STREETTREE)) -->
<!-- ``` -->

## GENUSSPECI (top 50)
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
df <- as.data.frame(table(ctree_clean$GENUSSPECI))
head(df[order(-df$Freq),],50)
```

## DBH_IN
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$DBH_IN, breaks=c(0,.1,.5,1,2,3,4,5,10,15,20,40,60,80,100),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$DBH_IN)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## LU
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(ctree_clean$LU)
t <- c(sum(is.na(ctree_clean$LU)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## CROWN_COMPACTNESS
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$CROWN_COMPACTNESS, breaks=c(0,seq(.00001, 4,.5)),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$CROWN_COMPACTNESS)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## HEIGHT_MAX
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$HEIGHT_MAX, breaks=c(0,.1, seq(10, 135, 10)),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$HEIGHT_MAX)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## HEIGHT_MEAN
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$HEIGHT_MEAN, breaks=c(0,.1, seq(10, 135, 10)),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$CROWN_COMPACTNESS)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## CROWN_AREA
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$CROWN_AREA, breaks=c(0,.1, 10, 100, 200, 400, 600, 1000),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$CROWN_COMPACTNESS)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## BLDG_AGE
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$BLDG_AGE, breaks=seq (80, 0, -10),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$BLDG_AGE)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## HU_DENS
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$HU_DENS, breaks=c(0, 100, 500, 1000, 1500, 2000, 3000, 6000, 9000,12000),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$HU_DENS)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

## RELBORDER_TREE
```{r echo=FALSE, comment=NA, cols.print=5, rows.print=50, max.print=1000}
t <- table(cut(ctree_clean$RELBORDER_TREE, breaks=seq(0, 1, 0.1),include.lowest = TRUE))
t <- c(sum(is.na(ctree_clean$RELBORDER_TREE)),t)
names(t) <- c("NA",names(t)[-1])
barplot(t)
t
```

